DALEX_TechQualityControl

### 2021-03-17 Scott_Modeling/DALEX.Rmd
Reorganizing things into folders

---
title: "DALEX_TechQualityControl"
author: "Scott Coffin"
date: "2/23/2021"
output: 
  html_document:
    code_folding: hide
    theme: journal
    toc: yes
    toc_float: yes
    toc_depth: 6
    number_sections: true
    includes:
      after_body: footer.html
  word_document:
    toc: yes
---
```{r global-options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      warning=FALSE, message=FALSE,time_it = TRUE) #report time to knit for all chunks

@@

```{r message=FALSE, warning=FALSE, include=FALSE}
# load required packages
library(rsample)
library(dplyr)
library(DALEX)
library(tidyverse)
library(tigerstats)
library(caret)
library(skimr)
library(ggeffects)
library(knitr)
library(doParallel)
library(modelplotr)
library(gridExtra)
```

```{r include=FALSE}
# Load finalized dataset.
aoc <- read_csv("AquaticOrganisms_Clean_final.csv", guess_max = 10000) #%>% 
  #mutate(ID = paste0("ID",row_number()))

@@

# final cleanup and factoring  
aoc_z$Species <- as.factor(paste(aoc_z$genus,aoc_z$species)) #must make value 'Species" (uppercase)
aoc_z$Group <- as.factor(aoc_z$organism.group) #must make value "Group"
aoc_z$Group <- fct_explicit_na(aoc_z$Group) #makes sure that species get counted even if they're missing a group

# save data object
#saveRDS(aoc_z, file = "aoc_z.Rda")
```
# Data Selection

@@

mp_classif_final_model <- model_performance(explainer_final_model)
mp_classif_final_model
```

```{r final model save}
#save model
saveRDS(final_model, file="final_rf_model.rds")
#load model
# final_model <- readRDS("final_rf_model.rds")
```

#### Performance
Performance metrics for the final model are below.

@@

##### What parameters bias the model?
Test residuals for size, dose, etc.

>>>>

---
title: "DALEX_TechQualityControl"
author: "Scott Coffin"
date: "2/23/2021"
output: 
  html_document:
    code_folding: hide
    theme: sandstone
    toc: yes
    toc_float: yes
    toc_depth: 6
    number_sections: true
  word_document:
    toc: yes
---
```{r global-options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      warning=FALSE, message=FALSE, echo = FALSE,
                      time_it = TRUE) #report time to knit for all chunks

@@

```{r message=FALSE, warning=FALSE}
# load required packages
library(rsample)
library(dplyr)
library(DALEX)
library(tidyverse)
library(tigerstats)
library(caret)
library(skimr)
library(ggeffects)
library(knitr)
library(doParallel)
library(modelplotr)
library(gridExtra)
```
# Setup
## Data Import
```{r}
# Load finalized dataset.
aoc <- read_csv("AquaticOrganisms_Clean_final.csv", guess_max = 10000) #%>% 
  #mutate(ID = paste0("ID",row_number()))

@@

# final cleanup and factoring  
aoc_z$Species <- as.factor(paste(aoc_z$genus,aoc_z$species)) #must make value 'Species" (uppercase)
aoc_z$Group <- as.factor(aoc_z$organism.group) #must make value "Group"
aoc_z$Group <- fct_explicit_na(aoc_z$Group) #makes sure that species get counted even if they're missing a group
```
## Data Selection

@@

mp_classif_final_model <- model_performance(explainer_final_model)
mp_classif_final_model
```
#### Performance
Performance metrics for the final model are below.

@@
